The JuliaHealth Observational Health Research Subecosystem

### 2024-01-17 paper.tex
Added Ergina reference to protocols in intro

% NOTE: I made this definition up on the fly using my expertise and familiarity with the space! :D /***//***//***/
Observational health research is the study and analysis of historical real world data to explore various cohorts found within such datasets to generate real world evidence to support applications within health-related domains.
Research within this space can investigate questions such as population health trends for a particular disease, health disparities within patient populations, and cost costs of care related to particular treatment procedures.
Due to the untapped potential of this space, over the past $20$ years, there have been several developments within the observational health research community to enable more effective research to be conducted within this field (such as the creation of interoperability standards and tool creation \cite{benderHL7FHIRAgile2013; mandelSMARTFHIRStandardsbased2016; overhage2012validation}).

>>>>

% NOTE: I made this definition up on the fly using my expertise and familiarity with the space! :D /***//***//***/
Observational health research is the study and analysis of historical real world data to explore various cohorts found within such datasets to generate real world evidence to support applications within health-related domains.
Research within this space can investigate questions such as population health trends for a particular disease, health disparities within patient populations, and cost costs of care related to particular treatment procedures.
Due to the untapped potential of this space, over the past $20$ years, there have been several developments within the observational health research community to enable more effective research to be conducted within this field (such as the creation of interoperability standards, protocols, and tool creation \cite{benderHL7FHIRAgile2013; mandelSMARTFHIRStandardsbased2016; overhage2012validation; ergina2013ideal}).
